Appendix to 'Detecting social information in a dense database of infants’ natural

### 2021-12-22 paper/preprint/appendix.Rmd
add code for roc curves, prf x age and location to appendix

```{r}
library(tidyverse)
library(ggplot2)
library(ggthemes)
```

@@

# ROC Curve

@@

load(here::here('data/preprocessed_data_2021/gold_sample_annotations2020-01-31.RData')) # human annotations

evaluate_detector <- function(truth, detection) {
  if (truth == TRUE) {
    if (truth == detection) return ("TP") # was face/wrist, detected face/wrist
    else return("FN") # was face/wrist, missed face/wrist
  }
  else {
    if (truth == detection) return("TN") # was not face/wrist, did not detect face/wrist
    else return("FP") # was not face/wrist, detected face/wrist
  }
}

@@

```{r}
roc_data <- gold_sample %>%
  select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
  mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
  right_join(all_gold_sample_frames_op) %>%
   mutate(hand_detected = hand_detected>0, face_detected = face_detected > 0) %>%
  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected)) %>%
  group_by(detection_threshold) %>%
  summarize(tpr_faces = return_tpr(face_eval_ketan), fpr_faces = return_fpr(face_eval_ketan), tpr_hands = return_tpr(hand_eval_ketan), fpr_hands = return_fpr(hand_eval_ketan))
```

@@

@@

# x-axis = False positive rate
# y-axis = True positive rate

@@

>>>>

```{r}
library(tidyverse)
library(ggplot2)
library(ggthemes)
library(egg)
```

@@

# Detection threshold estimations

@@

load(here::here('data/preprocessed_data_2021/gold_sample_annotations2020-01-31.RData')) # human annotations
```

```{r}
evaluate_detector <- function(truth, detection) {
  if (truth == TRUE) {
    if (truth == detection) return ("TP") # was face/wrist, detected face/wrist
    else return("FN") # was face/wrist, missed face/wrist
  }
  else {
    if (truth == detection) return("TN") # was not face/wrist, did not detect face/wrist
    else return("FP") # was not face/wrist, detected face/wrist
  }
}

@@

```{r}
roc_data <- gold_sample %>%
  select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
  mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
  right_join(all_gold_sample_frames_op) %>%
   mutate(hand_detected = hand_detected>0, face_detected = face_detected > 0) %>% # number = number of faces/hands detected
  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected)) %>%
  group_by(detection_threshold) %>%
  summarize(tpr_faces = return_tpr(face_eval_ketan), fpr_faces = return_fpr(face_eval_ketan), tpr_hands = return_tpr(hand_eval_ketan), fpr_hands = return_fpr(hand_eval_ketan))
```

@@

```
# OpenPose Error Analyses
```{r}
# join human and OP detections
gold_sample <- gold_sample %>%
  select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
  mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
  right_join(all_gold_sample_frames_op) %>%
  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected)) 
```

```{r}
# add age day bins to gold_sample
load(file=here::here('data/preprocessed_data_2021/all_vid_data_from_bbs_all_detections.RData')) # all detections
bin_size = 7 # days
min_age = min(all_vid_data$age_days, na.rm=TRUE) # 182
max_age = max(all_vid_data$age_days, na.rm=TRUE) # 966
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)

gold_sample <- gold_sample %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) 
```

```{r}
 return_prf = function(eval){
  tp=sum(eval == "TP")
  fp=sum(eval == "FP")
  fn=sum(eval == "FN")
  p = tp / (tp + fp)
  r = tp / (tp + fn)
  f=( 2 * p * r )/ (p + r)
  num_detect = length(eval)
  out <- data.frame(p,r,f,num_detect)
  return(out)
 }

@@

```{r}
prf_by_age_faces <-  gold_sample %>%
  group_by(child_id, age_day_bin) %>%
  do(return_prf(.$face_eval_ketan)) %>%
  filter(num_detect > 50)

prf_by_age_hands <-  gold_sample %>%
  group_by(child_id, age_day_bin) %>%
  do(return_prf(.$hand_eval_ketan)) %>%
  filter(num_detect > 50)
```

```{r}

prf_by_age_faces$age_day_bin = as.numeric(prf_by_age_faces$age_day_bin)

prf_by_age_hands$age_day_bin = as.numeric(prf_by_age_hands$age_day_bin)

ggplot(prf_by_age_faces, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=20, alpha=.1)  +
  ylim(0,1) +
  ylab('F-score - Face detection') +
  xlab('Age (months)') +
  theme(legend.position= 'none')

ggplot(prf_by_age_hands, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=20, alpha=.1)  +
  ylim(0,1) +
  ylab('F-score - Hand detection') +
  xlab('Age (months)') +
  theme(legend.position= 'none')

# p2 = ggplot(prf_by_age_faces, aes(x=age_day_bin, y=p, col=child_id, size=num_detect)) +
#   geom_point(alpha=.5) +
#   geom_smooth(span=10, alpha=.1)  +
#   ylim(0,1) +
#   ylab('Precision - Face detection')+
#   xlab('Age (months)') +
#   theme(legend.position= 'none')
# 
# p3 =ggplot(prf_by_age_faces, aes(x=age_day_bin, y=r, col=child_id, size=num_detect)) +
#   geom_point(alpha=.5) +
#   geom_smooth(span=10, alpha=.1)  +
#   ylim(0,1) +
#   ylab('Recall - Face detection')+
#   xlab('Age (months)') +
#   theme(legend.position= 'none')
# #
# ggarrange(p1,p2,p3)

@@

```{r}

```{r}
load(here::here('data/preprocessed_data_2021/saycam_metadata.RData')) # meta

num_videos_annotated = sum(!is.na(meta$Location))
videos_included = sum(!is.na(meta$Location) & meta$count_locations==1)
```

```{r}
gold_sample_by_location <- gold_sample %>%
  left_join(meta) %>%
  filter(!is.na(Location)) %>%
  filter(count_locations==1)

```{r}
prf_by_location_faces <-  gold_sample_by_location %>%
  group_by(Location) %>%
  do(return_prf(.$face_eval_ketan)) %>%
  filter(num_detect > 50)

prf_by_location_hands <-  gold_sample_by_location %>%
  group_by(Location) %>%
  do(return_prf(.$hand_eval_ketan)) %>%
  filter(num_detect > 50)
```

```{r}

ggplot(prf_by_location_faces, aes(x=Location, y=f, col=Location, size=num_detect)) +
  geom_point(alpha=.5) +
  ylab('F-score - Face detection') +
  theme(legend.position = 'none') +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylim(0,1)
```

```{r}
ggplot(prf_by_location_hands, aes(x=Location, y=f, col=Location, size=num_detect)) +
  geom_point(alpha=.5) +
  ylab('F-score - Hand detection') +
  theme(legend.position = 'none') +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylim(0,1)
```
